### 2012-03-15 docs/architecture/architecture.tex
edits

Whereas {\tt phys\_bc\_level\_array} provides a physical description
of the type of boundary, {\tt adv\_bc\_level\_array} describes the
{\em action} taken (e.g.\ reflect, extrapolate, etc.) for each
variable when filling boundaries.  {\tt adv\_bc\_level\_array} is
describes the boundary conditions that are in play for the advection
(hyperbolic) equations.  The form of this array is {\tt
  adv\_bc\_level\_array(0:ngrids,dim,2,nvar)} where the new component,
{\tt nvar}, allows for each state variable that lives on a grid to
have different boundary condition actions associated with it.  The
convention is that the first {\tt dm} variables in the \bclevel\ refer
to the velocity components, and the subsequent slots are for the other
standard variables described in the {\tt variables\_module}.  For
instance, to reference the boundary condition for density, one would
index with {\tt dm+rho\_comp}.  For temporary variables that are
created on the fly in the various routines in \maestro\ there may not
be a variable name in {\tt variables\_module} that describes the
temporary variable.  In this case, the special variables {\tt
  foextrap\_comp} and {\tt hoextrap\_comp} (first-order and high-order
extrapolation) are used.

>>>>

Whereas {\tt phys\_bc\_level\_array} provides a physical description
of the type of boundary, {\tt adv\_bc\_level\_array} describes the
{\em action} taken (e.g.\ reflect, extrapolate, etc.) for each
variable when filling boundaries.  {\tt adv\_bc\_level\_array} 
specifically describes the boundary conditions that are in play for the advection
(hyperbolic) equations.  The form of this array is {\tt
  adv\_bc\_level\_array(0:ngrids,dim,2,nvar)} where the additional component,
{\tt nvar}, allows for each state variable that lives on a grid to
have different boundary condition actions associated with it.  The
convention is that the first {\tt dm} variables in the \bclevel\ refer
to the velocity components, and the subsequent slots are for the other
standard variables described in the {\tt variables\_module}.  For
instance, to reference the boundary condition for density, one would
index with {\tt dm+rho\_comp}.  For temporary variables that are
created on the fly in the various routines in \maestro\ there may not
be a variable name in {\tt variables\_module} that describes the
temporary variable.  In this case, the special variables {\tt
  foextrap\_comp} and {\tt hoextrap\_comp} (first-order and high-order
extrapolation) are used.
